Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-12 docs/00-manuscripts/ieee/ieee-manuscript.tex
remove trailing komma in table

% filter methods
\begin{table}[b!]
\centering
\caption[t]{List of filter methods used in this work}
\begingroup\footnotesize
\begin{adjustbox}{width={0.48\textwidth},totalheight={\textheight},keepaspectratio}
	\begin{tabular}{lll}
		\\
		Name                                         & Group                             & Ref.               \\
		\toprule
		Linear correlation (Pearson)                 & univariate, linear, correlation   & \cite{pearson1901} \\
		Information gain                             & univariate, non-linear, entropy   & \cite{quinlan1986} \\
		Minimum redundancy, maximum relevance        & multivariate, non-linear, entropy & \cite{zhao2013}    \\
		Carscore                                     & multivariate, linear, correlation & \cite{zuber2011}   \\
		Relief                                       & multivariate, linear, entropy,    & \cite{kira1992}    \\
		Conditional minimal information maximization & multivariate, linear, entropy     & \cite{fleuret2004}
	\end{tabular}
\end{adjustbox}
\endgroup\label{tab:filter-methods}
\end{table}

>>>>

% filter methods
\begin{table}[b!]
\centering
\caption{List of filter methods used in this work}
\label{tab:filter-methods}
\begingroup\footnotesize
\begin{adjustbox}{width={0.48\textwidth},totalheight={\textheight},keepaspectratio}
	\begin{tabular}{lll}
		\\
		Name                                         & Group                             & Ref.               \\
		\toprule
		Linear correlation (Pearson)                 & univariate, linear, correlation   & \cite{pearson1901} \\
		Information gain                             & univariate, non-linear, entropy   & \cite{quinlan1986} \\
		Minimum redundancy, maximum relevance        & multivariate, non-linear, entropy & \cite{zhao2013}    \\
		Carscore                                     & multivariate, linear, correlation & \cite{zuber2011}   \\
		Relief                                       & multivariate, linear, entropy    & \cite{kira1992}    \\
		Conditional minimal information maximization & multivariate, linear, entropy     & \cite{fleuret2004}
	\end{tabular}
\end{adjustbox}
\endgroup
\end{table}
